Data paper

### 2015-02-27 papers/data_paper/datapaper.tex
fri

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
\caption{The bottom panel shows 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
from the literature, in addition to that measured by us.
In ordinate, for each galaxy, we plot the average value $\langle \log(n_{\rm sph}) \rangle$ of (the logarithm of) the individual measurements. 
In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Red points are from \cite{grahamdriver2007}, 
blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
white points are from \cite{rusli2013}, orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compn}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
\caption{The bottom panel shows 52 galaxies for which at least one measurement 
of the major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
from the literature, in addition to that measured by us.
In ordinate, for each galaxy, we plot the average value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
of (the logarithm of) the individual measurements. 
In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Red points are from \cite{grahamdriver2007}, 
blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(R_{\rm e}^{\rm maj}) - \langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compre}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
\caption{The bottom panel shows 51 galaxies for which at least one measurement 
of the bulge apparent magnitude $m_{\rm sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
from the literature, in addition to that measured by us. 
$3.6~\rm \mu m$ magnitudes were converted to $K$-band magnitudes.
In ordinate, for each galaxy, we plot the average value $\langle m_{\rm sph} \rangle$ 
of the individual measurements. 
In abscissa we plot the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, 
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the equivalent-axis).
In the top panel, the white histogram shows the distribution of $m_{\rm sph} - \langle m_{\rm sph} \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compmag}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
\caption{The bottom panel shows 49 galaxies for which at least one measurement 
of the bulge effective surface brightness $\mu_{\rm e,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
from the literature, in addition to that measured by us. 
$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm e,sph} \rangle$ 
of the individual measurements. 
In abscissa we plot the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, 
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\mu_{\rm e,sph} - \langle \mu_{\rm e,sph} \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compmue}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
\caption{The bottom panel shows 49 galaxies for which at least one measurement 
of the bulge central surface brightness $\mu_{\rm 0,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
from the literature, in addition to that measured by us. 
$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm 0,sph} \rangle$ 
of the individual measurements. 
In abscissa we plot the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, 
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\mu_{\rm 0,sph} - \langle \mu_{\rm 0,sph} \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compmu0}
\end{center}
\end{figure}

@@

>>>>

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
\caption{Bottom panel: 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(n_{\rm sph}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
Each data point corresponds to an individual measurement from: 
\citeauthor{grahamdriver2007}~(\citeyear{grahamdriver2007}, red points);  
\citeauthor{laurikainen2010}~(\citeyear{laurikainen2010}, blue points); 
\citeauthor{sani2011}~(\citeyear{sani2011}, green points);  
\citeauthor{vika2012}~(\citeyear{vika2012}, yellow points);
\citeauthor{beifiori2012}~(\citeyear{beifiori2012}, gray points); 
\citeauthor{rusli2013}~(\citeyear{rusli2013}, white points); 
\citeauthor{lasker2014data}~(\citeyear{lasker2014data}, orange points). 
Black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to the measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively, 
corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres}.}
\label{fig:compn}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
\caption{Bottom panel: 52 galaxies for which at least one measurement of the bulge major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compre}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
\caption{Bottom panel: 51 galaxies for which at least one measurement of the bulge apparent magnitude $m_{\rm sph}$ 
-- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
$3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
The average value $\langle m_{\rm sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmag}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the bulge effective surface brightness $\mu_{\rm e,sph}$ 
-- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
$K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm e,sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmue}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the bulge central surface brightness $\mu_{\rm 0,sph}$ 
-- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
$K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm 0,sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmu0}
\end{center}
\end{figure}

@@

{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }
